Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-19 intro.tex
[bib] More marginally relevant refs added at the 2nd para of intro.

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) across the system. As shown in Fig.~\ref{fig:cut-and-join}, we first prepare the system at the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve. Various quantities are used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. The authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution. In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with its boundary critical exponent.

@@

It would therefore be interesting to connect two different CFTs in the ``cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}. There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study their entanglement properties. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the compact Boson case, it is controlled by the ratio of the compactification radii, and in the free lattice Boson case by the ratio of masses. We expect it to be tunable in a realistic experimental setting.

@@

The rest of the paper is organized as follows.

In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization.

In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally we conclude in Sec.~\ref{sec:conclusion}.

>>>>

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. \cite{hegde_quench_2015,francica_local_2016,lupo_transient_2016,lee_spatiotemporal_2016,chung_memory_2016,kibble-zurek_2017,sacramento_edge_2016,vasseur_expansion_2015,mazza_overlap_2016}The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) across the system. As shown in Fig.~\ref{fig:cut-and-join}, we first prepare the system at the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve. Various quantities are used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. The authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution. In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with its boundary critical exponent.

@@

It would therefore be interesting to connect two different CFTs in the ``cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. It can be realized as interface of two free compact boson theories with different compactification radii\cite{bachas_permeable_2002}. There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study their entanglement properties. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the compact boson case, it is controlled by the ratio of the compactification radii, and in the free lattice boson case by the ratio of masses. We expect it to be tunable in a realistic experimental setting.

@@

The rest of the paper is organized as follows. In Sec.~\ref{sec:bosonic_conformal_interface}, we introduce the general formalism for permeable conformal interface and its lattice realization. In Sec.~\ref{sec:analytic_numerics}, we analytically evaluate the free energy associated with fidelity and Loschmidt echo, and present the numerical results for comparison. We discuss our results and related experimental works in Sec.~\ref{sec:disc}. Finally we conclude in Sec.~\ref{sec:conclusion}.
